%Gabriel Zea CV
%
%Uses moderncv package
%
%To avoid problems make sure the texlive-fonts texlive-latexextra packages are installed
%
%ChangeLog
%	2.11.08	Version inicial
%       3.5.09 update

\documentclass[10pt,letter]{moderncv}
\moderncvtheme[grey]{casual}                 

% character encoding
\usepackage[utf8]{inputenc}   
\usepackage{enumerate}
\usepackage{verbatim}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{ Camilo }
\familyname{ Martinez }
\title{Desarrollador Multimedia y Web}
\address{San Jose 382 piso 2. Buenos Aires, Argentina}{C1076AAH}    
\phone{(54) 11 3927 4969}
%\phone{(54) 15 3927 4969}                     
\email{cmart@decolector.net}                     
\extrainfo{http://martinez-zea.info} % optional, remove the line if not wanted
\extrainfo{http://decolector.net}
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the 
%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}

% slanted small caps (only with roman family; the sans serif font doesn't exists :-()
%\usepackage{slantsc}
%\DeclareFontFamily{T1}{myfont}{}
%\DeclareFontShape{T1}{myfont}{m}{scsl}{ <-> cork-lmssqbo8}{}
%\usefont{T1}{myfont}{m}{scsl}Testing the font

% command and color used in this document, independently from moderncv 
\definecolor{see}{rgb}{0.0,0.5,0.5}% for web links
\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}% for text subscripts

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle

\section{Sumario}
{}{Experiencia en conceptualizaci\'{o}n y desarrollo t\'{e}cnico de aplicaciones multimedia y proyectos interactivos para arte, publicidad y eventos. Desarrollo de aplicaciones web con bases de datos. Montaje e integraci\'{o}n de servicios web 2.0. Capacidad de integrar tecnolog\'{i}as de software y hardware en soluciones para proyectos de interacci\'{o}n f\'{i}sica, multimedia y en red. Conocimientos en herramientas y entornos de c\'{o}digo abierto para desarrollo de software y hardware.  
}{}{}{}{}

%%% Educacion
\section{Formaci\'{o}n}
\cventry{2000 - 2005}{Maestro en Artes Pl\'{a}sticas con enfasis en Nuevas Tecnolog\'{i}as }{ Escuela de Artes Pl\'{a}sticas, Universidad Nacional de Colombia}{}{}{}

%%%Skills
\section{Habilidades}

\begin{comment}
\begin{itemize}
	\item[A] Lenguajes de Programacion y entornos: Python, Processing, Openframeworks ( C++ ).
	\item[A] Hardware: Arduino, Electr\'{o}nica digital, Eagle. 
	\item[Administradores de Versiones:] Git, Mercurial, Subversion.
	\item[Servidores Web:] Apache, Charokee.
	\item[Protocolos de Comunicacion:] Osc, TCP/IP, RS232.
	\item[Sistemas Operativos:] Unix/Linux, OSX.
	\item[Administracion:] ssh, ftp, bash.
	\item[Graficos:] Blender 3D, Photoshop, GIMP, Inkscape.
\end{itemize}
\end{comment}

\cventry{}{Programaci\'{o}n}{Python, Processing, Openframeworks, C++}{}{}{}
\cventry{}{Administradores de Versiones}{Git, Mercurial, Subversion}{}{}{}
\cventry{}{Hardware}{Galeria laLocalidad}{Bogot\'{a}}{}{} 
\cventry{}{Aplicaciones Web}{Django}{}{}{}
\cventry{}{Web}{HTML, CSS, Javascript}{}{}{} 
\cventry{}{Servidores}{Apache, Cherokee, Osc, FTP}{}{}{}
\cventry{}{Administracion}{SSH, ftp, MySqlAdmin, bash}{}{}{}
\cventry{}{Sistemas Operativos}{Unix/Linux, OSX}{}{}{}
\cventry{}{Gr\'{a}ficos}{Blender 3D, Photoshop - Gimp, Inkscape}{}{}{}
\cventry{}{Video - Animaci\'{o}n}{Blender 3D, Final Cut}{}{}{}

%%Group
\section{Proyectos}
% 2008
\cventry{2010}{Miler Lagos Portfolio}{Django, HTML, Javascript, CSS}{\url{http://milerlagos.com}}{}{}
\cventry{2009}{Clap}{Arduino, Eagle, Prototipado y produccion de hardware}{\url{http://claproject.co.cc}}{}{}
\cventry{2009}{Julian Jaramillo homepage }{Django, HTML, Javascript, CSS}{\url{http://julianjaramillo.net}}{}{}
\cventry{2009}{Galeria 980}{Django, HTML, Javascript, CSS}{\url{http://nueveochenta.com}}{}{}
\cventry{2008}{Matik Matik homepage}{Django, HTML, Javascript, CSS}{\url{http://matik-matik.com}}{}{}

\section{Idiomas}
\cventry{}{Ingl\'{e}s}{Avanzado}{}{}{}
\cventry{}{Portugu\'{e}s}{B\'{a}sico}{}{}{}

\section{Otros}

\cventry{2007 - 2011}{Grupo Martinez - Zea}{ colectivo de artistas trabajando con tecnologia}{\url{http://martinez-zea.info}}{}{}
\end{document}

